### 2017-08-03 Paper01_EnthalpyAndCrystallization.tex
Results - Fragility - Put equtions on own line and started rewrite of section

Variable heating rate \acrshort{dsc} for both the bulk and film \MgZnCa~ was used to establish the fragility of the system. Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ \cite{Busch1998} for both the bulk and film. The fragility $m$ could then be calculated from the relationship $D^{*}=590/(m-16)$ \cite{Angell2002, Wei2014}.

>>>>

Using the isochronic \acrshort{dsc} data the fragility of the \MgZnCa~ system could be established for both the bulk and film. Numerical solutions where used to fit the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.

\begin{equation}
	\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T_{g}-T_{0}})}
	\label{equ:VFT}
\end{equation}

Where $\tau_{0}$ is a pre-exponential factor, $D^{*}$ is the liquid Fragility parameter, and $T_{0}$ is the \gls{vft} temperature where the barrier to flow becomes infinite.

The fragility $m$ could then be calculated from Equation \ref{equ:dStar} \cite{Angell2002, Wei2014}.

\begin{equation}
	D^{*}=590/(m-16)
	\label{equ:dStar}
\end{equation}
